Hospitalizations for psychiatric conditions among adolescents during the COVID-19 pandemic

### 2021-09-29 psy_peds_3.Rmd
age at diagnosis

clinical_test <- clinical_table[, c("patient_num", "n_hospitalisation", "days_since_admission")] %>% 
  inner_join(distinct(observation_table_ado, patient_num, days_since_admission, age_time_diagnosis), 
            by = c("patient_num", "days_since_admission"))

@@

observation_table_ado <- clinical_table %>% 
  inner_join(observation_table[, c("patient_num", "days_since_admission")], 
             by = c("patient_num", "days_since_admission"))

@@

all_codes_ado <- all_codes %>% 
   filter(age_time_visit >= 11 & age_time_visit <= 17)

>>>>

clinical_test <- clinical_table[, c("patient_num", "n_hospitalisation", "days_since_admission")] %>% 
  inner_join(distinct(observation_table_ado, patient_num, days_since_admission, age_time_diagnosis), 
            by = c("patient_num", "days_since_admission")) %>% 
  select(patient_num, n_hospitalisation, age_time_diagnosis)

@@

@@

all_codes_ado <- all_codes %>% 
   filter(age_time_diagnosis >= 11 & age_time_diagnosis <= 17)
